Using Sorghum as an outgroup to find syntenic regions in Maize: regenerating

### 2017-12-14 SubGenome Analysis.Rmd
Migrating to data-as-packages format
Also enabling easier transition between windows/linux platforms by updating file paths.

```{r importSynMapData, include=FALSE}
load("~/git/SubGenomes/Data/SavedObjects/loadedData.RData")

# source("~/git/SubGenomes/R/loadData.R")
# source("~/git/SubGenomes/R/cleanData.R")
source("~/git/SubGenomes/R/functions.R")
source("~/git/SubGenomes/R/do.R")

@@

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('./Data/Images/High expressing genes tend to vary.png')
```

@@

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('./Data/Images/Low Expressing Genes tend to stay low.png')
```

@@

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('./Data/Images/Pollen is different.png')
```

@@

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('./Data/Images/High-low variation.png')
```

@@

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('./Data/Images/Top fold-change genes.png')
```

>>>>

```{r importSynMapData, include=FALSE}
source("./R/do.R")

@@

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('./data/Images/High expressing genes tend to vary.png')
```

@@

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('./data/Images/Low Expressing Genes tend to stay low.png')
```

@@

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('./data/Images/Pollen is different.png')
```

@@

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('./data/Images/High-low variation.png')
```

@@

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('./data/Images/Top fold-change genes.png')
```
